---
title: "Introduction to SC19080"
author: "Jianrui Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SC19080}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

__SC19080__ is a simple R package developed for the final homework of the 'Statistical Computing' course in 2020 fall. Three functions are considered, namely, $L1$, $Max\_abs$ and $Max \_ abs\_cor$.

## Usage of $L1$
```{r, include=FALSE}
L1 = function(){
  
  itemp <- function(y, offset, parms, wt) {
    if (is.matrix(y) && ncol(y) > 1)
       stop("Matrix response not allowed")
    if (!missing(parms) && length(parms) > 0)
        warning("parameter argument ignored")
    if (length(offset)) y <- y - offset
    sfun <- function(yval, dev, wt, ylevel, digits ) {
		  paste("  mean=", format(signif(yval, digits)),
			", MSE=" , format(signif(dev/wt, digits)),
			sep = '')
    }
    environment(sfun) <- .GlobalEnv
    list(y = c(y), parms = NULL, numresp = 1, numy = 1, summary = sfun)
  }

  etemp <- function(y, wt, parms) {
    wmean <- median(y)
    rss <- sum(abs(y-wmean))
    list(label = wmean, deviance = rss)
  }

  stemp <- function(y, wt, x, parms, continuous){
    
    n <- length(y)
    
    if (continuous) {
        
        goodness = rep(0,n-1)
        direction = rep(0,n-1)
        
        for(i in 1:(n-1)){
            lmedian = median(y[1:i])
            rmedian = median(y[(i+1):n])
            goodness[i] = 1/log(sum(abs(y[1:i]-lmedian)) + sum(abs(y[(i+1):n]-rmedian)) )
            direction[i] = sign(lmedian - rmedian)
        }
        
        list(goodness = goodness, direction = direction)
        
    } 
    else {
        
        ux = sort(unique(x))
        ymean  <- tapply(y,x,mean)
        ymean_data = as.data.frame(ymean)
        ord <- order(ymean)
        m <- length(ord)
        
        goodness = rep(0,m-1)
        direction = rep(0,m-1)
        
        INDEX = rep(0,n)

        for(i in 1:n){
            INDEX[i] = which(rownames(ymean_data) == x[i])
        }
        

        for(i in 1:m-1){
            index_left = which(INDEX %in% ord[1:i])
            y_left = y[index_left]
            y_right = y[-index_left]
            lmedian = median(y_left)
            rmedian = median(y_right)
            goodness[i] = 1/log(sum(abs(y_left-lmedian)) + sum(abs(y_right-rmedian)) )
        }
        
        
        list(goodness= goodness, direction = ux[ord])
    }
  }

  list(eval = etemp, split = stemp, init = itemp)
}

library(kedd)

Max_abs = function(X){
    p = ncol(X)
    Max=0
    for(i in 1:p){
      for(j in 2:p){
        if(j>i){
          if(abs(X[i,j])>Max){
            Max = abs(X[i,j])
          }
        }
      }
    }
    return(Max)
}

Max_abs_cor= function(n = 30, p = 200, replicate = 500){

  n = n
  p = p
  m = replicate
  x = rep(0,m)

  for(i in 1:m){
    X = matrix(rnorm(p*n), nrow = n, ncol = p)
    x[i] = SC19080::Max_abs(cor(X))
  }

  kedd::dkde(x, deriv.order = 0)
}
```
The $rpart$ function provides an implementation of CART in R. And the $L1$ provides the $L_1$ splitting function in $rpart$, which can be directly applied in the argument $method$ of $rpart$. For an example, see below.


```{r}
library(rpart)
library(rpart.plot)
mystate <- data.frame(state.x77, region=state.region)
names(mystate) <- casefold(names(mystate))
fit1 <- rpart(murder ~ population + illiteracy + income + life.exp +hs.grad + frost + region, data = mystate, method = L1(), minsplit = 10)
rpart.plot(fit1)
```

This example is an imitation of that in the vignette '[User Written Splitting Functions](https://cran.r-project.org/web/packages/rpart/vignettes/usercode.pdf)'. The source code of $L1$ is also modified from this vignette. For more descriptions of $rpart$, please refer to [this](https://cran.r-project.org/web/packages/rpart/index.html).

What should be pointed out is that here I take advantage of the package $rpart.plot$. For an introduction, see [this](http://www.milbo.org/rpart-plot/prp.pdf). 



## Usage of $Max\_abs$

This is an easy function used in $Max \_ abs\_cor$. It just calculates the maximum of the absolute value of a correlation matrix except the diagonal elements. For an example, see below.

```{r}
data = matrix(rnorm(5*4), nrow = 5, ncol = 4)
cor(data)
Max_abs(cor(data))
```

We can easily find that $Max\_abs$ gives our desired result.

## Usage of $Max\_abs\_cor$

This function provides an estimation of the maximum absolute sample correlation coefficient of standard normal distribution in high dimensions, which is done by generating samples and an Gaussian kernel estimation. It takes advantage of the package $kedd$ and returns the same object as $dkde$ does.


```{r}
set.seed(12345)
result = Max_abs_cor(n = 30, p = 200, replicate = 500)
plot(result)
```


My initial intention is to provide the figure 1 in Prof. Fan's [paper](https://orfe.princeton.edu/~jqfan/papers/06/SIS.pdf) on Sure Independence Screening.
